Spatial Reasoning and Statistical Graphics

### 2014-10-17 Paper/Draft1/TestingVisualAptitude.Rnw
More comment responses.

\comment{could we also refer to the fact that these tests have been long established (maybe with references to earlier tests or updates?)}
The advantage of using tests from the Kit of Factor Referenced Cognitive tests \citep{ekstrom1976manual} is that the tests are extremely well studied \citep{voyer1995magnitude} and comparison data are available from the validation of these factors.
\comment{the well studied reference list needs to be a bit more extensive ... do you know this book by Michel Hersen?}
The card rotation, paper folding, and figure classification tests have been validated using different populations, many of which are demographically similar to Iowa State students (naval recruits, college students, late high-school students, and 9th grade students).

>>>>

\comment{could we also refer to the fact that these tests have been long established (maybe with references to earlier tests or updates?) \textit{Yes, definitely. I'll pull up some references for that too...}}
The advantage of using tests from the Kit of Factor Referenced Cognitive tests \citep{ekstrom1976manual} is that the tests are extremely well studied \citep{voyer1995magnitude} and comparison data are available from the validation of these factors.
\comment{the well studied reference list needs to be a bit more extensive ... do you know this book by Michel Hersen?\\\textit{I was working on it yesterday along with trying to validate the general idea that reading graphics requires certain spatial abilities. It's definitely a work in progress. I haven't seen that book before, but I'm not at all surprised it exists.}}
The card rotation, paper folding, and figure classification tests have been validated using different populations, many of which are demographically similar to Iowa State students (naval recruits, college students, late high-school students, and 9th grade students).
